Differentially Private Bayesian Inference

### 2018-03-29 main.tex
format update

%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}
% \usepackage[utf8]{inputenc}
% \usepackage[english]{babel}
% Recommended, but optional, packages for figures and better typesetting:
\usepackage{mathtools,amssymb}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mdframed}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}
% \renewcommand\qedsymbol{$\blacksquare$}
% \theoremstyle{plain}
%   \newtheorem{thm}{Theorem}
% \theoremstyle{definition}
%   \newtheorem*{proof1}{Proof of Theorem \ref{Fermat}}
% Attempt to make hyperref and algorithmic work together better:
% \newenvironment{proofof}[1]{\par
%   \pushQED{\qed}%
%   \normalfont \topsep6\p@\@plus6\p@\relax
%   \trivlist
%   \item[\hskip\labelsep
%         \bfseries
%     Proof of #1\@addpunct{.}]\ignorespaces
% }{%
%   \popQED\endtrivlist\@endpefalse
% }
% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}
\input{macros}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2018}

\begin{document}

\twocolumn[
\icmltitle{Differentially Private Bayesian Inference}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2018
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
\end{abstract}

\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{multline*}
\Delta_{g}u = 
\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|\\
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}.
\end{multline*}

@@

\subsubsection{Security Analysis}
It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\mathsf{PrivInfer}$. For adjacent data set $||x,y||_1 = 1$:
\begin{equation*}
\begin{split}
& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
& =\frac
{\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
{\frac
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
& = \left(\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp\left(\frac
{\epsilon (u(x,r) - u(y,r))}
{2 \Delta_{g}u}
\right) \\
& \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& \leq
exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp(\epsilon).
\end{split}
\end{equation*}

Then, $\frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

@@

\subsubsection{Security Analysis}
We will then prove that exponential mechanism with local sensitivity is non-differentialy private.
\begin{equation*}
\begin{split}
& \frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]} \\
& = exp\left(
\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} - 
\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
\right)  \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
\right) \\
& = \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}.
\end{split}
\end{equation*}

@@

Then we can have:
\begin{equation*}
\begin{split}
& exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)}))\\
& > exp(\frac{\epsilon}{2} * 2) \\
& = exp(\epsilon),
\end{split}
\end{equation*}
i.e.
\begin{equation*}
\begin{split}
\frac{P[\mathsf{PrivInfer}(x,u,R) = r]}{P[\mathsf{PrivInfer}(y,u,R) = r]}
& > exp(\epsilon).
\end{split}
\end{equation*}

@@

% \twocolumn{
\begin{equation*}
\boxed{
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
}
\end{equation*}

@@

From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:
\vspace*{9.5cm}

@@

\begin{equation*}
\begin{split}
\because \quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)\\
					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
\therefore \quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)),\\
					& \quad \quad \quad \quad \quad \quad \quad \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					&< \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					& > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1))\\
					& \quad \quad \quad = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
\end{split}
\end{equation*}

@@

	\begin{equation*}
	\begin{split}
	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
						= &\frac
						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
						= \frac
						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
						= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
	\end{split}
	\end{equation*}

	Then, we proof the property in cases of $\lambda > 0$ and $\lambda < 0$:

@@

\subsection{Sliding Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\mathcal{M}_E(x, u, \mathcal{R})$ $Pr[]$
\end{lem}
\begin{proof}
\end{proof}

@@

\bibliographystyle{icml2018}
\bibliography{example_paper}

>>>>

\input{macros}

\title{\textbf{Notes of DP - Bayesian Inference}\\}
\author{Jiawen \textsc{Liu}}

\begin{document}
\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

Exponential mechanism with global sensitivity selects and outputs a candidate $r \in R$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})$:
\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})},
\end{equation*}
where global sensitivity is calculated by:
\begin{equation*}
\Delta_{g}u = 
\max_{\{|x',y'| \leq 1;x',y'\in \mathcal{X}^n\}}\max_{\{r\in R\}}
|\hlg(\bysinfer(x'), r) - \hlg(\bysinfer(y'), r)|
\end{equation*}

@@

\subsubsection{Security Analysis}
It can be proved that exponential mechanism with global sensitivity is $\epsilon$-differentially private. We denote the $\bysinfer$ with privacy mechanism as $\privinfer$. For adjacent data set $||x,y||_1 = 1$:
\begin{equation*}
\begin{split}
\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
& =\frac
{\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}}
{\frac
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}} \\
& = \left(\frac
{exp(\frac{\epsilon u(x,r)}{2 \Delta_{g}u})}
{exp(\frac{\epsilon u(y,r)}{2 \Delta_{g}u})}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp\left(\frac
{\epsilon (u(x,r) - u(y,r))}
{2 \Delta_{g}u}
\right)
\cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& \leq
exp(\frac{\epsilon}{2}) \cdot exp(\frac{\epsilon}{2}) \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{g}u})}
\right)\\
& = exp(\epsilon).
\end{split}
\end{equation*}

Then, $\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} \geq exp(-\epsilon)$ can be obtained by symmetry.

@@

\subsubsection{Security Analysis}
We will then prove that exponential mechanism with local sensitivity is non-differentialy private.
\begin{equation*}
\begin{split}
\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]} 
& = exp\left(
\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} - 
\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)}
\right)  \cdot
\left(\frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}
\right) \\
& = \frac
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(x,r)}{2 \Delta_{l}u(x)} 
+ \frac{\epsilon u(y,r')}{2 \Delta_{l}u(y)})}
{\sum\limits_{r' \in R}\ exp(\frac{\epsilon u(y,r)}{2 \Delta_{l}u(y)} 
+ \frac{\epsilon u(x,r')}{2 \Delta_{l}u(x)})}.
\end{split}
\end{equation*}

@@

Then we can have:
\begin{equation*}
\begin{split}
& exp(\frac{\epsilon}{2} (\frac{u(x,r) + u(y,r)}{\Delta_{l}u(y)} - \frac{u(x,r) + u(y,r)}{\Delta_{l}u(x)}))\\
& > exp(\frac{\epsilon}{2} * 2) \\
& = exp(\epsilon),
\end{split}
\end{equation*}
i.e.
\begin{equation*}
\begin{split}
\frac{P[\privinfer(x,u,R) = r]}{P[\privinfer(y,u,R) = r]}
& > exp(\epsilon).
\end{split}
\end{equation*}

@@

% \twocolumn{
\begin{equation*}
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
\end{equation*}

@@

From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:

@@

\begin{equation*}
\begin{split}
\because \footnote{the symbol of $\because$ here means because}
\quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)\\
					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
\therefore \footnote{the symbol of $\therefore$ here means therefore}
\quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)),\\
					& \quad \quad \quad \quad \quad \quad \quad \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					&< \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					& > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1))\\
					& \quad \quad \quad = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
\end{split}
\end{equation*}

@@

	\begin{equation*}
	\begin{split}
	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
		= &\frac
		{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
		{\int_{S}{} \frac{1}{2}e^{-|z|} dz} \\
		= &\frac
		{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
		{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
		= & \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}} \\
		= & \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}\\
	\end{split}
	\end{equation*}

	Then, we proof the dilation property in cases of $\lambda > 0$ and $\lambda < 0$ separately:

@@

\subsection{Sliding Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the sliding property holds:

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}] \leq e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2}
\end{equation*}

\end{lem}

\begin{proof}
\end{proof}

@@

% \bibliographystyle{icml2018}
% \bibliography{example_paper}
